\documentclass[paper=letter, 11pt]{article}
\usepackage{worksheet}

\school{University of Wisconsin - Madison}
\course{Calculus II}
\title{Worksheet 10}
\subtitle{Taylor Polynomials}

\usepackage{tcolorbox}

\begin{document}
\maketitle

\begin{tcolorbox}[title=Definition: Taylor Polynomials,fonttitle=\bfseries\rmfamily]
	The \textbf{Taylor polynomial} of a function $y = f(x)$ of degree $n$ at a point $a$ is the polynomial:
	
	\[ T^a_n f(x) = f(a) + f'(a)(x - a) + \dfrac{f''(a)}{2!}(x-a)^2 + \,\cdots\, + \dfrac{f^(n)(a)}{n!}(x - a)^n \]
	
	The \textbf{Taylor series} of a function $y = f(x)$ centered at $a = 0$ is the infinite sum:
	
	\[ T_{\infty} f(x) = f(0) + f'(0)x + \dfrac{f''(0)}{2!}x^2 + \dfrac{f'''(0)}{3!}x^3 + \,\cdots\, + \dfrac{f^(n)(0)}{n!}x^n +\, \cdots \]
\end{tcolorbox}

Calculate the derivatives of the following functions and look for a pattern.  Use this pattern to calculate the \textit{Taylor series} for the following functions.\bigskip

\Prob $e^x$ \vfill

\Prob $\sin x$ \vfill

\Prob $\sqrt{1 + x}$ \vfill

\newpage

\begin{center}
\begin{minipage}{0.8\textwidth}
\begin{tcolorbox}[title=Fundamental Taylor Series Formulas,fonttitle=\bfseries\rmfamily]
Write out the formulas for the following Taylor series.  You will be expected to know how to calculate these by the definitions, but also memorized.

\begin{flalign*}
T_{\infty}\,e^x &= &\\\\
T_{\infty}\,\sin x &= &\\\\
T_{\infty}\,\cos x &= &\\\\
T_{\infty}\,\dfrac{1}{1-x} &= &\\\\
T{_\infty}\,\ln(1 - x) &= &\\
\end{flalign*}

\end{tcolorbox}
\end{minipage}
\end{center}

\section*{Taylor Series by Substitution}

Suppose you know the Taylor series for $f(x)$, then you can calculate the Taylor series for $f(3x)$ or $f(x^2)$, etc, by simply substituting $3x$ or $x^2$ into your Taylor series.\\

For example, we know:

\[ T_{\infty} e^x = 1 + x + \dfrac{x^2}{2!} + \frac{x^3}{3!} + \,\cdots\, +  \frac{x^n}{n!} + \, \cdots \]

So to find the Taylor series for $e^{3x}$ and $e^{-x^2}$ is a simple as a substitution:

\begin{align*}
T_{\infty} e^{3x} &= 1 + (3x) + \frac{(3x)^2}{2!} + \frac{(3x)^3}{3!} + \,\cdots\, + \frac{(3x)^n}{n!} + \,\cdots \\
 &= 1 + 3x + \frac{9x^2}{2!} + \frac{27x^3}{3!} + \,\cdots\, + \frac{3^n x^n}{n!} + \,\cdots \\
 & \\
T_{\infty} e^{-x^2} &= 1 + (-x^2) + \frac{(-x^2)^2}{2!} + \frac{(-x^2)^3}{3!} + \,\cdots\, + \frac{(-x^2)^n}{n!} + \,\cdots \\
 &= 1 - x^2 + \frac{x^4}{2!} - \frac{x^6}{3!} + \,\cdots\, + \frac{(-1)^nx^{2n}}{n!} + \,\cdots \\
\end{align*}

\newpage

Use the substitution method to find a Taylor series for the following problems.

\Prob $\dfrac{1}{1 - x^2}$\vfill

\Prob $\ln(1 - 2x^3)$\vfill

\Prob $\sin(2x^4)$\vfill

\newpage

\section*{Calculating Taylor Series by Multiplying by $x^n$}

If you know the Taylor series for $f(x)$ then the Taylor series for $x^nf(x)$ is obtained by multiplying $T_{\infty}f(x)$ by $x^n$.  Use this technique for the following.\bigskip

\Prob $\dfrac{3}{2 - x}$. \quad Hint:\,\,$\dfrac{3}{2 - x} = \dfrac{3}{2}\cdot \dfrac{1}{1 - x/2}$.\vfill

\Prob $\frac{x}{2 - x^2}$\vfill

\Prob $x\ln(2 + 2x)$\vfill

\newpage

\section*{Adding Taylor Series}

Calculate the Taylor series for the following.\bigskip

\Prob $\sinh(x)$. \quad Recall: $\sinh(x) = \frac{1}{2}(e^x - e^{-x})$.\vfill

\Prob $\dfrac{1}{x^2 - 3x + 2}$. \quad Hint: PFD!\vfill

\Prob $\dfrac{1 + x}{1 - x}$.\vfill

\newpage



\newpage


\end{document}