\documentclass[paper=letter, 11pt]{article}
\usepackage{../worksheet}

\school{University of Wisconsin - Madison}
\course{Calculus II}
\title{Exam 2 Review}
\subtitle{}

\usepackage{tcolorbox}
\newcommand{\IVProb}[1]{
	\begin{minipage}{0.5\textwidth}
		\Prob Find a solution to the initial value problem:
	\end{minipage}%
	\begin{minipage}{0.5\textwidth}
		\begin{align*}
			#1
		\end{align*}
	\end{minipage}
}

\begin{document}
\maketitle

\section*{Differential Equations}

\IVProb{
	\frac{dy}{dx} &= \Big(1 + y^2\Big)e^x && y(0) = 0 && \\
}\vfill

\IVProb{
	\frac{dy}{dx} &=  \left(y^2 - 1\right)\cos(x) && y(0) = 1 && \\
}\vfill


\IVProb{
	x\frac{dy}{dx} + 2y &= -\frac{\sin(x)}{x}  && y\left(\frac{\pi}{2}\right) = 1 && \\
}\vfill

\newpage

\Prob Find the general solution to the differential equation: \quad $\DS \frac{1}{2x}\frac{dy}{dx} = y + e^{x^2}$.\vfill

\Prob Find a particular solution to the initial value problem: \quad $\DS \frac{1 + x^3}{3x^2}\frac{dy}{dx} = 1 - y(x)$.\vfill

\Prob Find the exact solution to the initial value problem $\DS\frac{dy}{dx} = -2xy$ where $y(0) = 1$.  Then use Euler's method with step size $\Delta x = 0.1$ to estimate $y(0.3)$.\vfill

\newpage

\Prob A 100 litre vat of water begins with an algae concentration of 1,000 organisms per litre. 
Suppose that the algae naturally reproduce at a rate of five percent per minute and die
at a rate of four percent per minute. If the vat is being drained at a rate of one litre
per minute, what will the algae concentration be ten minutes from now? You should
assume that the algae are uniformly distributed in the vat. Remember to define your variables with units.\vfill

\Prob A tank with 200 gallons of brine solution contains 40 lbs of salt. A concentration of
2 lb/gal is pumped in at a rate of 4 gal/min. The concentration leaving the tank is
pumped out at a rate of 4 gal/min. Find a differential equation describing the amount
of salt in the tank at time t.\vfill

\Prob The rate at which a certain drug is eliminated from the bloodstream is proportional to
the amount of the drug in the bloodstream. A patient now has 45 mg of the drug in his
bloodstream. The drug is being administered to the patient intravenously at a constant
rate of 5 milligrams per hour. Write a differential equation modeling the situation.\vfill

\Prob In the absence of predators the population of mosquitoes in a certain area would increase
at a rate proportional to its current population and its population would double every
three weeks. There are 250,000 mosquitoes in the area initially when a flock of birds
arrives that eats 80,000 mosquitoes per week. How many mosquitoes remain after two
weeks?

\section*{Taylor Polynomials/Series}

\Prob For $f(x) = x^4 + x + 1$, find the degree three Taylor polynomial of $f(x)$ around 1.  That is, find $T^1_3\,f(x)$.\vfill

\Prob Hadrubal has designed a rocket.  While proving mathematically that it won't ex

\end{document}